---
title: "Bayesian A/B Testing in R \n"
author: Adam Rosenblit & David Denton
date: April 26, 2019
output:
  revealjs::revealjs_presentation:
    transition: slide
    theme: blood
    highlight: zenburn
    center: true
---
```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri("logo4.png"), 
               alt = 'logo', 
               style = 'background:none; border:none; box-shadow:none; position:relative;')
```

### Company Overview
* Established in 2012
* Leading online widget supplier
* Excellent sales growth during first four years
* Sales began to decrease in 2016
    + Complicated web order form

## A slide with an ordered list

We're going to talk about this stuff:

1. Data
2. Bayes
3. The airspeed velocity of unladen swallows


## A slide with an unordered list

- First important thing
- Second important thing

## A slide with code (and a table)

```{r message=FALSE}
library(tidyverse)

mtcars1 <- mtcars %>%
  group_by(cyl, gear) %>%
  tally()
```

```{r echo = FALSE}
knitr::kable(mtcars1, caption = 'A count of cars', format = 'html') %>%
    kableExtra::kable_styling(bootstrap_options = c('striped'))
```

## A slide with a plot

```{r, cars, fig.cap = "A scatterplot", echo = FALSE}
plot(cars)
```
