---
title: "Bayesian A/B Testing in R \n"
author: Adam Rosenblit & David Denton
date: April 26, 2019
output:
  revealjs::revealjs_presentation:
    transition: slide
    theme: blood
    highlight: zenburn
    center: true
---
```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri("logo4.png"), 
               alt = 'logo', 
               style = 'background:none; border:none; box-shadow:none; position:relative;')
```

### Company Overview
* Established in 2012
* Leading online widget supplier
* Excellent sales growth during first four years
* Sales began to decrease in 2016
    + Complicated web order form
    + Increasing number of orders from mobile devices
    
## Existing Sales Funnel
```{r message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
library(ggthemes)
gg <- read_csv('ab_data_2.csv') %>%
    filter(test_flag == 'pre_test') %>%
    group_by(page_num) %>%
    summarise(total_sessions = n_distinct(session_id)) %>%
    ungroup() %>%
    mutate(pct_total_sessions = total_sessions/first(total_sessions)) %>%
    ggplot(aes(x = page_num, y = pct_total_sessions, fill = as_factor(pct_total_sessions))) +
    geom_bar(stat = 'identity') +
    geom_text(nudge_y = .05, aes(label = paste0(round(pct_total_sessions*100, 2), '%')), size = 5) +
    theme_economist() + scale_fill_economist() +
    theme(legend.position = 'none') + theme(text= element_text(size = 14)) + 
    theme(axis.title = element_text(face = 'bold')) +
    xlab('Page Number') + ylab('Percent of Sessions') 
    
    
gg
```


## A slide with an ordered list

We're going to talk about this stuff:

1. Data
2. Bayes
3. The airspeed velocity of unladen swallows


## A slide with an unordered list

- First important thing
- Second important thing


## A slide with code (and a table)

```{r message=FALSE}
library(tidyverse)

mtcars1 <- mtcars %>%
  group_by(cyl, gear) %>%
  tally()
```

```{r echo = FALSE}
knitr::kable(mtcars1, caption = 'A count of cars', format = 'html') %>%
    kableExtra::kable_styling(bootstrap_options = c('striped'))
```


## A slide with a plot

```{r, cars, fig.cap = "A scatterplot", echo = FALSE}
plot(cars)
```
